
---
title: "EDPS 845 Assignment 1"
author: "Mingying (Emily) Zheng"
output: pdf
---

## Overview

Demonstrate your mastery of concepts and procedures covered in *An Introduction to R*, chapters 1 through 9. See Appendix A for examples.

Complete this assignment by responding to each question below using your own original code, in addition to answering any questions. Follow Google's [R coding conventions](https://google.github.io/styleguide/Rguide.xml), and use [R markdown](http://rmarkdown.rstudio.com/index.html) formatting for your responses, with example R code written as

```{r, eval = FALSE}
# Comment within some example code
#HERE you can write any r codes.
x<- rnorm (100)
mean(x)
```

Your file should have an Rmd extension, and you should check that it compiles to HTML using the *Knit* command in RStudio (this runs `knitr::knit()` on the file). Note that you can already *Knit* this file to see how it works.

## Exercises

### Chapter 1

1. Show that you can access the home page for the HTML R help menu, as well as help files for individual functions.

```{r, eval = FALSE}
# The help function in HTML format by running
help.start()

# The specific named help function, for example solve OR covariance, the commands are
help (solve)
help (cov)

# An alternatives are
?solve
?cov

# ?? allows searching for help in various ways (such as the referred topics in different contexts)
##?? can be used to search for the topics beyond the fundemental functions by R.
###?? can be very useful in finding any related topics you are interested in.
??solve
??cov
??IRT

#The examples on a help topic can be run by
example(solve)
example(cov)


# Windows version of R, we can use this option for help.
?help
```

2. Demonstrate correct and incorrect naming of R objects.

```{r, eval = FALSE}
#File names
## File Names should end in .R and be meaningful.
### Good file name
myname.R
### Bad file name
myna.R

# Correct naming--normally all alphanumeric symbols are allowed plus"."
## if it starts with ‘.’ the second character must not be a digit.
### R commands are case sensative.
vars10<-c(1, 3, 5, 7, 9, 2, 4, 6, 8, 10)
presmoothing.formula <-function (x, ...).
A5<-c(10, 20, 30, 40, 50)
a5<-c(11, 22, 33, 44, 55)
myname <- "Emily"
EDPS845allusers <- c("Tony",  "Yage",  "Jayden",  "Mingying(Emily)", "Catherine (katie)", "Pamela (Pam)", "Liuhan (Sophie)",  "Mark", "Brooke", "Chansuk", "Benjamin (Ben)")
EDPS845students <- c("Yage",  "Jayden",  "Mingying(Emily)", "Catherine (katie)", "Pamela (Pam)", "Liuhan (Sophie)",  "Mark", "Brooke", "Chansuk", "Benjamin (Ben)")
# Incorrect naming
10vars<-c(1, 3, 5, 7, 9, 2, 4, 6, 8, 10)
.6v<-c(1, 2, 3, 4, 5, 6)
.10<-c(1, 3, 5, 7, 9, 2, 4, 6, 8, 10)
_v10<-c(1, 3, 5, 7, 9, 2, 4, 6, 8, 10)
_v<-c(1, 3, 5, 7, 9, 2, 4, 6, 8, 10)

```

3. How do you list all available objects in the R workspace? And how do you remove individual objects?

```{r, eval = FALSE}
# List available objects in the R workspace
ls()
#OR
objects()

# Remove individual objects, here vars10, x, EDPS845allusers.

rm(vars10, x, EDPS845allusers)
```

### Chapter 2

1. Create and index a vector using a logical, integer, negative integer, and character vector.
```{r, eval = FALSE}
x1 <- c(4, -11, 2001)
#OR
assign("x2", c(1, -2, 3, -4, 5, -6))


```

2. Create and index a vector using a logical, integer, negative integer, and character vector.
```{r, eval = FALSE}


```
3. Create a simple data frame containing a numeric variable, character variable, and factor with at least 3 levels. Use the data frame to demonstrate how R codes and handles missing data. 
```{r, eval = FALSE}


```
### Chapter 3

1. Demonstrate how to check and change the modes and attributes of R objects.
```{r, eval = FALSE}


```
### Chapter 4

1. Complete the exercise on page 17, where you calculate 95% confidence intervals for state mean incomes.
```{r, eval = FALSE}


```
2. In what order are the levels of ordered factors stored in?
```{r, eval = FALSE}


```
### Chapter 5

1. Create an array with dimensions `c(3, 6, 2)` and use it to demonstrate array indexing.
```{r, eval = FALSE}


```
2. Create a two dimensional array of 100 integers sampled with replacement from the vector 1:20, and use an index array to set the diagonal values to 0.
```{r, eval = FALSE}


```
3. Construct the same array using the `array()` function and using a vector with the `dim()` set. Prove they are the same.
```{r, eval = FALSE}


```
4. Use your array from 5.1, and another with the same dimensions, to demonstrate how arithmetic works with arrays.
```{r, eval = FALSE}


```
5. Show how to clear the dimensions of an array.
```{r, eval = FALSE}


```
### Chapter 6

1. Demonstrate the different ways of subsetting a list.
```{r, eval = FALSE}


```
2. What is the difference between giving multiple lists to `list()` versus `c()`?
```{r, eval = FALSE}


```
3. How do data frames in R relate to lists?
```{r, eval = FALSE}


```
4. What is the purpose of `attach()`?
```{r, eval = FALSE}


```
### Chapter 7

1. Demonstrate the different approaches to reading in data from an external file.
```{r, eval = FALSE}


```
### Chapter 8

1. Demonstrate the use of distribution functions to simulate data and calculate probabilities and quantiles.
```{r, eval = FALSE}


```
2. Simulate data from a t distribution and check their normality.
```{r, eval = FALSE}


```
### Chapter 9

1. What is the difference between `if() else` and `ifelse()`?
```{r, eval = FALSE}


```
2. Demonstrate the use of a `for()` loop.

```{r, eval = FALSE}


```
